### 2020-01-23 defesa/tex/chapter/definicoes.tex
wip

\begin{equation}\label{eq:norm2}
||u||_2 = \sqrt{u^{T}u}.
\end{equation}
The elliptical norm, also known as weighted norm, takes a $2$ by $2$ positive definite matrix as its parameter. This matrix can be seen as a linear transformation of the Euclidean norm. The elliptical norm of $u \in\R^2$ is defined as

\begin{equation}
||u||_{Q} = \sqrt{u^{T}Qu},
\end{equation}
where $Q$ is a $2$ by $2$ positive definite matrix. Note that the elliptical norm, when taking $Q$ to be the identity matrix, becomes the Euclidean norm.

@@

An ellipse is a curve which is categorized, along with the parabola and the hyperbola, as a conic section. 
They get this name because conic sections are curves resulted from the intersection of a right circular cone in $\R^3$ with a plane \cite{brannan:geometry}. From that definition, an equation which describes any conic section is given as follows
\begin{equation}\label{equation:quadratic_form}
Ax^2 + Bxy + Cy^2 + Dx + Ey + F = 0,
\end{equation}
where $A,B,C,D,E,F \in \R$ are fixed and $x, y \in \R$. Distinguishing an ellipse from the other conic sections ca be done using the condition given by \autoref{eq:conic_ellipse}. More details about conic sections can be found in \citeonline{ayoub}.
\begin{equation}\label{eq:conic_ellipse}
4AC - B^2>0.
\end{equation}

Assuming the center of an ellipse is $c \in \R^2$, then \autoref{equation:quadratic_form} can be rewritten as a quadratic form as follows
\begin{equation}
(p-c)^{T}Q(p-c) = 1,
\end{equation}
with $p \in \R^2$ and $Q$ being a $2$ by $2$ positive definite matrix which carries the parameters of the ellipse. From \autoref{equation:quadratic_form}, $Q$ can be defined as follows
\[
Q=
\left( {\begin{array}{cc}
	A & \frac{B}{2} \\
	\frac{B}{2} & C \\
	\end{array} } \right).
\]
Note that asking $Q$ to be positive definite is the same as asking $4AC-B^2$ to be positive. This makes us arrive at the following definition of the ellipse.

@@

\subsection{Axis-parallel}

@@

\[
Q=
\left( {\begin{array}{cc}
    \frac{1}{a^2} & 0 \\
    0 & \frac{1}{b^2} \\
    \end{array} } \right),
\]

\noindent then, starting from \autoref{def:ellipse}, we can obtain the following equation

\begin{align*}
        (p-c)^{T}Q(p-c) = 1 & \Rightarrow \\
    (\frac{p_x-c_x}{a^2}, \frac{p_y-c_y}{b^2})^{T}(p_x-c_x, p_y-c_y) = 1 & \Rightarrow
 \end{align*}
 \begin{equation}\label{equation:pellipse}
  \frac{(p_x-c_x)^2}{a^2} + \frac{(p_y-c_y)^2}{b^2} = 1,
 \end{equation}
where $a$ and $b$ are the semi-major and semi-minor shape parameters, respectively.

@@

Another way to represent ellipses, which will be useful in some occasions, is through writing it as a curve, function of the angle with its major-axis (see \autoref{fig:ellipse_params}).

@@

    \caption{The ellipse as a parametric curve.}
%    \input{tex/figures/ellipse_definition.tex}
   	\includegraphics[scale=.4]{tex/figures/ellipse_definition.pdf}
    \fautor
    \label{fig:ellipse_params}
\end{figure}

Let $c \in \R^2$ be the center of an ellipse with shape parameters $(a,b) \in \R^2_{>0}$. Then $\gamma : [0, 2\pi] \mapsto \R^2$ defines a curve which maps every angle onto a point on the ellipse and it is defined as follows
\begin{equation}\label{eq:parametric_ellipse}
\gamma(t) = \left\{
\begin{array}{l}
x(t)= a\cos{t} + c_x,\\
y(t)=b\sin{t} + c_y.
\end{array}
\right.
\end{equation}

Consider an ellipse with shape parameters $(a, b)\in\R^2_{>0}$ centered at the origin, and a line represented by the equation $y=mx+c$, with $m, c\in \R$. Suppose that this line intersects the ellipse at a least one point. Plugging the line's equation into \autoref{equation:pellipse}, it is possible to obtain the distance between the intersection points. The final expression is given by
\begin{equation}\label{eq:dist_line_ellipse}
D(m, c)=\dfrac{\sqrt{(a^2m^2+b^2-c^2)(4a^2b^2(1+m^2))}}{(a^2m^2+b^2)},
\end{equation}
with $D : \R^2 \mapsto \R_{\ge0}$ being a function of the line parameters $(m, c)$. It is also possible to see that, when $m$ is fixed, $D(m, c)^2$ is a parabola, and that $D(m, c)$ is maximized at $c=0$. From that, we can conclude that if $m$ is fixed, the line that has the most distant intersection points with an ellipse is the one that passes through the origin; and also, that $D(m, c)$ attains every value in the range $[0, D(m, 0)]$. 
Following that, we define a function $L:m\mapsto\R_{>0}$ that describes the maximum squared distance between the points of the intersection of an ellipse with a line with a fixed angular coefficient:
\begin{equation}\label{eq:function-l}
L(m):= D(m, 0)^2 = \dfrac{(a^2m^2+b^2)(4a^2b^2(1+m^2))}{(a^2m^2+b^2)^2}.
\end{equation}
It is possible, by calculating the derivatives, to conclude that $L$ has its maximum at $x=0$, is increasing in $[0, \infty)$, is decreasing in $(-\infty\, 0]$, and attains every value in the interval $(4b^2, 4a^2]$. Notice that $L$ never hits $4b^2$ because that is the distance between the intersection of the ellipse with a vertical line.
In \autoref{fig:L-function-plot}, an example of function $L$ is shown with $(a, b) = (2, 1)$.

@@

	\caption{Plot of function $L$ in the interval $[-7, 7]$.}
	\includegraphics[scale=.5]{tex/figures/L-function-plot}
	\fautor
	\label{fig:L-function-plot}
\end{figure}

\subsection{Non-axis-parallel}

A non-axis-parallel ellipse centered at $(c_x, c_y)\in\R^2$ can also be described by \autoref{def:ellipse}. Nonetheless, a simpler equation is going to be used here. Besides the center, and the shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$, an angle of rotation $\theta \in \R$ is given. This new parameter represents the angle between the $x$-axis and the major-axis of the ellipse, this can be seen on \autoref{fig:rotated_ellipse} where the dashed lines represent the ellipse's axes and the angle between the major-axis and the $x$-axis is displayed.

@@

Another important property of ellipses is shown on \autoref{fig:rotated_ellipse}. The two angles of rotation between the major-axis and the $x$-axis ($\theta$ and $\theta+\pi$) are actually equivalent--they produce the same ellipse. This symmetry is true for any angle of rotation, which means that $\theta$ is equivalent to $\theta+k\pi$, $k\in\mathbb{Z}$. Therefore, it is possible to conclude that to represent any ellipse, it is enough to specify the domain of $\theta$ to be $[0, \pi)$.

@@

A complex number is composed of a real part added to an imaginary part which is a multiple of the imaginary unit $i = \sqrt{-1}$. This is expressed as $a + bi$, with $a, b \in \R$. Because $z$ is composed of two real numbers, the complex number system can be visualized on $\R^2$ as shown on \autoref{fig:complex-numbers}. This is also a good way to visualize Euler's Formula, as it can be also seen on \autoref{fig:complex-numbers}, which says that any complex number can be written in terms of its radius and polar angle as follows:
\begin{equation}
z = re^{i\theta}=r(\cos{\theta} + i\sin{\theta}),
\end{equation}
with $r$ being the length of the vector determined by the point $z$ on the complex plane and $\theta = angle(z)$ being its polar angle. Note that $angle$ is a function from $\mathbb{C}$ to $[0, 2\pi)$.
\begin{figure}[ht]
	\centering
	\def\svgwidth{\columnwidth}
	\includegraphics[scale=.4]{tex/figures/complex_numbers}
	\caption{The representation of a complex number on two dimensions.}
	\label{fig:complex-numbers}
\end{figure}

The complex conjugate is another important operator that is utilized later. Let $z = a + bi \in \mathbb{C}$, then we refer to $\bar{z}$ as the complex conjugate of $z$ and it is defined as:
\begin{equation}
\bar{z} = a - bi.
\end{equation}
Finally, we need to state two observations about the angles of $-z$ and $\bar{z}$ with respect to the angle of $z$, this will be useful later on \autoref{chapter:e3p}.
\begin{align}
angle(\bar{z}) = 2\pi-angle(z)\\
angle(-z) = \pi + angle(z),
\end{align}
checking the validity of these two equalities can be done by just observing the symmetry between the points defined by $z, \bar{z},$ and $-z$ on the plane.

@@

The famous Abel-Ruffini Theorem (a proof can be seen in \citeonline{skopenkov2015}) states that for polynomials of degree higher than four, there is no closed formula\footnote{A finite number of $+, -, \times, \div, \sqrt{}$.} to determine their roots. Fortunately, a numerical approach exists for higher-degree polynomials which works really well in practice.

 In \citeonline[p.~195]{horn} a theorem is presented which says that for every univariate polynomial of degree $n$, there exists a companion matrix which is a $n\times n$ matrix, such that its eigenvalues are the zeros of that polynomial. For example, the companion matrix of a degree-$5$ polynomial written as \autoref{eq:poly} is given by
 \begin{equation}
 \left[\begin{array}{ccccc}
 0 & 1 & 0 & 0 & 0\\
 0 & 0 & 1 & 0 & 0\\
 0 & 0 & 0 & 1 & 0\\
 0 & 0 & 0 & 0 & 1\\
 -\dfrac{a_0}{a_5} & -\dfrac{a_1}{a_5} & -\dfrac{a_2}{a_5} & -\dfrac{a_3}{a_5} & -\dfrac{a_4}{a_5}
 \end{array}\right].
 \end{equation}

 Finding every eigenvalue of a matrix can be done using the QR algorithm, which runs in $\bigO(n^3)$ and uses $\bigO(n^2)$ memory. A very complete introduction to this algorithm can be found on \citeonline{watkins:2008}. The idea is to convert the input matrix to the Hessenberg form, after that, the matrix preserves its form through the iterations and under some assumptions, convergence to the eigenvalues is achieved.
 Also, in \citeonline{barel} it is pointed that companion matrices are already in the Hessenberg form, making the Hessenberg conversion step unnecessary. This and other properties are used in \citeonline{barel} on the development of a $\bigO(n^2)$ algorithm for the specific case of companion matrices.

 In practice, LAPACK's ZGEEV routine is utilized--the user guide can be found in \citeonline{lapack}--which is an implementation of the QR algorithm that returns every eigenvalue of a complex matrix.

@@

The same definition found in \citeonline[p.~150]{powell} for real trigonometric polynomials is given here. They are also referred to as truncated Fourier Series in \citeonline{boyd:2006} and are given by
\begin{equation}\label{eq:trig_poly}
p_n(\theta) = \sum_{k=0}^{n} a_k\cos(k\theta) + \sum_{k=1}^{n} b_k\sin(k\theta).
\end{equation}
We say that $p_n: \R \mapsto \R$ as defined by \autoref{eq:trig_poly} is a $n$-degree real trigonometric polynomial. An important property is stated in \citeonline[p.~150]{powell}, it says that a $n$-degree polynomial can have up to $2n$ distinct roots on the interval $[0, 2\pi)$. It also says that a function written in the format
$$\begin{array}{cc}\cos^j{\theta}\sin^k{\theta} & \quad j, k \in \mathbb{Z}_+ \end{array},$$
can be transformed into a real trigonometric polynomial of degree $j+k$. Therefore, the following expression also represents a $n$-degree real trigonometric polynomial
\begin{equation}\label{eq:trig_poly_2}
\sum_{0 \le j+k \le n}c_{j,k}\cos^j{\theta}\sin^k{\theta},
\end{equation}
for some $\{c_{j,k} \in \R: 0 \le j+k \le n\}$.

>>>>

\begin{equation*}
||u||_2 = \sqrt{u^{T}u}.
\end{equation*}
The elliptical norm, also known as weighted norm, takes a $2$ by $2$ positive definite matrix as its parameter. This matrix can be seen as a linear transformation of the Euclidean norm. The elliptical norm of $u \in\R^2$ is defined as

\begin{equation*}
||u||_{Q} = \sqrt{u^{T}Qu},
\end{equation*}
where $Q$ is a $2$ by $2$ positive definite matrix. Note that the elliptical norm, when taking $Q$ to be the identity matrix, becomes the Euclidean norm.

@@

An ellipse is a curve which is categorized, along with the parabola and the hyperbola, as a conic section. 
They get this name because conic sections are curves resulted from the intersection of a right circular cone in $\R^3$ with a plane \cite{brannan:geometry}. From that definition, an equation which describes any conic section is given as follows
\begin{equation}\label{equation:quadratic_form}
Ax^2 + Bxy + Cy^2 + Dx + Ey + F = 0,
\end{equation}
where $A,B,C,D,E,F \in \R$ are fixed and $x, y \in \R$. Distinguishing an ellipse from the other conic sections ca be done using the condition given by 
\begin{equation*}
4AC - B^2>0.
\end{equation*}
More details about conic sections can be found in \citeonline{ayoub}.

Assuming the center of an ellipse is $c \in \R^2$, then \autoref{equation:quadratic_form} can be rewritten as a quadratic form as follows
\begin{equation*}
(p-c)^{T}Q(p-c) = 1,
\end{equation*}
with $p \in \R^2$ and $Q$ being a $2$ by $2$ positive definite matrix which carries the parameters of the ellipse. From \autoref{equation:quadratic_form}, $Q$ can be defined as follows
\[
Q=
\left( {\begin{array}{cc}
	A & \frac{B}{2} \\
	\frac{B}{2} & C \\
	\end{array} } \right).
\]
Note that asking $Q$ to be positive definite is the same as asking $4AC-B^2$ to be positive. This makes us arrive at the following definition of the ellipse.

@@

\subsection{Axis-parallel ellipse}

@@

\[
Q=
\left( {\begin{array}{cc}
    \frac{1}{a^2} & 0 \\
    0 & \frac{1}{b^2} \\
    \end{array} } \right),
\]
then, starting from \autoref{def:ellipse}, we can obtain the following equation

 \begin{align}\label{equation:pellipse}
 \begin{aligned}
 (p-c)^{T}Q(p-c) &= 1 & \Rightarrow \\
 (\frac{p_x-c_x}{a^2}, \frac{p_y-c_y}{b^2})^{T}(p_x-c_x, p_y-c_y) &= 1 & \Rightarrow\\
  \frac{(p_x-c_x)^2}{a^2} + \frac{(p_y-c_y)^2}{b^2} &= 1,&
   \end{aligned}
 \end{align}
where $a$ and $b$ are the semi-major and semi-minor shape parameters, respectively.

@@

Another way to represent ellipses, which will be useful in some occasions, is through writing it as a curve function of the angle with its major-axis (see \autoref{fig:ellipse_params}).

@@

    \caption{The ellipse as a parametric curve.}
%    \input{tex/figures/ellipse_definition.tex}
   	\includegraphics[scale=.36]{tex/figures/ellipse_definition.pdf}
    \fautor
    \label{fig:ellipse_params}
\end{figure}

Let $c \in \R^2$ be the center of an ellipse with shape parameters $(a,b) \in \R^2_{>0}$. Then $\gamma\colon[0, 2\pi]\mapsto\R^2$ defines a curve which maps every angle onto a point on the ellipse and it is defined as follows
\begin{equation}\label{eq:parametric_ellipse}
\gamma(t) = \left\{
\begin{array}{l}
x(t)= a\cos{t} + c_x,\\
y(t)=b\sin{t} + c_y.
\end{array}
\right.
\end{equation}

Consider an ellipse with shape parameters $(a, b)\in\R^2_{>0}$ centered at the origin, and a line represented by the equation $y=mx+c$, with $m, c\in \R$. Suppose that this line intersects the ellipse at least at one point. Plugging the line's equation into \autoref{equation:pellipse}, it is possible to obtain the distance between the intersection points. The final expression is given by
\begin{equation*}\label{eq:dist_line_ellipse}
D(m, c)=\dfrac{\sqrt{(a^2m^2+b^2-c^2)(4a^2b^2(1+m^2))}}{(a^2m^2+b^2)},
\end{equation*}
with $D : \R^2 \mapsto \R_{\ge0}$ being a function of the line parameters $(m, c)$. It is also possible to see that, when $m$ is fixed, $D(m, c)^2$ is a parabola, and that $D(m, c)$ is maximized at $c=0$. From that, we can conclude that if $m$ is fixed, the line that has the most distant intersection points with an ellipse is the one that passes through the origin; and also, that $D(m, c)$ attains every value in the range $[0, D(m, 0)]$. 
Following that, we define a function $L:m\mapsto\R_{>0}$ that describes the maximum squared distance between the points of the intersection of an ellipse with a line with a fixed angular coefficient:
\begin{equation}\label{eq:function-l}
L(m):= D(m, 0)^2 = \dfrac{(a^2m^2+b^2)(4a^2b^2(1+m^2))}{(a^2m^2+b^2)^2}.
\end{equation}
It is possible, by calculating the derivatives, to conclude that $L$ has its maximum at $x=0$, is increasing in $[0, \infty)$, is decreasing in $(-\infty\, 0]$, and attains every value in the interval $(4b^2, 4a^2]$. Notice that $L$ never hits $4b^2$ because that is the distance between the intersection of the ellipse with a vertical line.
In \autoref{fig:L-function-plot}, an example of function $L$ is shown with $(a, b) = (2, 1)$.

@@

	\caption{Plot of function $L$ in the interval $[-7, 7]$.}
	\includegraphics[scale=.4]{tex/figures/L-function-plot}
	\fautor
	\label{fig:L-function-plot}
\end{figure}

\subsection{Non-axis-parallel ellipse}

A non-axis-parallel ellipse centered at $(c_x, c_y)\in\R^2$ can also be described by \autoref{def:ellipse}. Nonetheless, a simpler equation is going to be used here. Besides the center, and the shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$, an angle of rotation $\theta \in \R$ is given. This new parameter represents the angle between the $x$-axis and the major-axis of the ellipse, this can be seen on \autoref{fig:rotated_ellipse}, where the dashed lines represent the ellipse's axes and the angle between the major-axis and the $x$-axis is displayed.

@@

Another important property of ellipses is shown on \autoref{fig:rotated_ellipse}. The two angles of rotation between the major-axis and the $x$-axis ($\theta$ and $\theta+\pi$) are actually equivalent -- they produce the same ellipse. This symmetry is true for any angle of rotation, which means that $\theta$ is equivalent to $\theta+k\pi$, $k\in\mathbb{Z}$. Therefore, it is possible to conclude that to represent any ellipse, it is enough to specify the domain of $\theta$ to be $[0, \pi)$.

@@

A complex number is composed of a real part added to an imaginary part which is a multiple of the imaginary unit $i = \sqrt{-1}$. This is expressed as $a + bi$, with $a, b \in \R$. Because $z$ is composed of two real numbers, the complex number system can be visualized on $\R^2$ as shown on \autoref{fig:complex-numbers}. This is also a good way to visualize Euler's Formula, as it can be also seen on \autoref{fig:complex-numbers}, which says that any complex number can be written in terms of its radius and polar angle as follows:
\begin{equation*}
z = re^{i\theta}=r(\cos{\theta} + i\sin{\theta}),
\end{equation*}
with $r$ being the length of the vector determined by the point $z$ on the complex plane and $\theta = angle(z)$ being its polar angle. Note that $angle$ is a function from $\mathbb{C}$ to $[0, 2\pi)$.
\begin{figure}[ht]
	\centering
	\def\svgwidth{\columnwidth}
	\includegraphics[scale=.37]{tex/figures/complex_numbers}
	\caption{The representation of a complex number on two dimensions.}
	\label{fig:complex-numbers}
\end{figure}

The complex conjugate is another important operator that is utilized later. Let $z = a + bi \in \mathbb{C}$, then we refer to $\bar{z}$ as the complex conjugate of $z$ and it is defined as:
\begin{equation*}
\bar{z} = a - bi.
\end{equation*}
Finally, we need to state two observations about the angles of $-z$ and $\bar{z}$ with respect to the angle of $z$, this will be useful later on \autoref{chapter:e3p}:
\begin{align*}
angle(\bar{z}) = 2\pi-angle(z),\\
angle(-z) = \pi + angle(z).
\end{align*}
Checking the validity of these two equalities can be done by just observing the symmetry between the points defined by $z, \bar{z},$ and $-z$ on the plane.

@@

The famous Abel-Ruffini Theorem (a proof can be seen in \citeonline{skopenkov2015}) states that for polynomials of degree higher than four, there is no closed formula\footnote{A formula with a finite number of $+, -, \times, \div, \sqrt{}$.} to determine their roots. Fortunately, a numerical approach exists for higher-degree polynomials which works really well in practice.

 In \citeonline[p.~195]{horn} a theorem is presented which says that for every univariate polynomial of degree $n$, there exists a companion matrix which is a $n\times n$ matrix, such that its eigenvalues are the zeros of that polynomial. For example, the companion matrix of a degree-$5$ polynomial written as \autoref{eq:poly} is given by
 \begin{equation*}
 \left[\begin{array}{ccccc}
 0 & 1 & 0 & 0 & 0\\
 0 & 0 & 1 & 0 & 0\\
 0 & 0 & 0 & 1 & 0\\
 0 & 0 & 0 & 0 & 1\\
 -\dfrac{a_0}{a_5} & -\dfrac{a_1}{a_5} & -\dfrac{a_2}{a_5} & -\dfrac{a_3}{a_5} & -\dfrac{a_4}{a_5}
 \end{array}\right].
 \end{equation*}

 Finding every eigenvalue of a matrix can be done using the QR algorithm, which runs in $\bigO(n^3)$ and uses $\bigO(n^2)$ memory. A very complete introduction to this algorithm can be found on \citeonline{watkins:2008}. The idea is to convert the input matrix to the Hessenberg form, after that, the matrix preserves its form through the iterations and, under some assumptions, convergence to the eigenvalues is achieved.
 Also, in \citeonline{barel} it is pointed that companion matrices are already in the Hessenberg form, making the Hessenberg conversion step unnecessary. This and other properties are used in \citeonline{barel} on the development of a $\bigO(n^2)$ algorithm for the specific case of companion matrices.

 In practice, LAPACK's ZGEEV routine is utilized (the user guide can be found in \citeonline{lapack}), which is an implementation of the QR algorithm that returns every eigenvalue of a complex matrix.

@@

The same definition found in \citeonline[p.~150]{powell} for real trigonometric polynomials is given here. They are also referred to as truncated Fourier Series in \citeonline{boyd:2006} and are given by
\begin{equation}\label{eq:trig_poly}
p_n(\theta) = \sum_{k=0}^{n} a_k\cos(k\theta) + \sum_{k=1}^{n} b_k\sin(k\theta).
\end{equation}
We say that $p_n: \R \mapsto \R$ as defined by \autoref{eq:trig_poly} is a $n$-degree real trigonometric polynomial. An important property is stated in \citeonline[p.~150]{powell}, which says that a $n$-degree polynomial can have up to $2n$ distinct roots on the interval $[0, 2\pi)$. It also says that a function written in the format
$$\begin{array}{cc}\cos^j{\theta}\sin^k{\theta}, & \quad j, k \in \mathbb{Z}_+, \end{array}$$
can be transformed into a real trigonometric polynomial of degree $j+k$. Therefore, the following expression also represents a $n$-degree real trigonometric polynomial
\begin{equation}\label{eq:trig_poly_2}
\sum_{0 \le j+k \le n}c_{j,k}\cos^j{\theta}\sin^k{\theta},
\end{equation}
for some $\{c_{j,k} \in \R: 0 \le j+k \le n\}$.

### 2020-01-23 defesa/tex/chapter/mcd.tex
wip

An instance of MCD is given by a set of $n$ demand points $\Pp:=\{p_1, \dots, p_n\}$, with $p_j\in\R^2$; a set of weights $\Ww:=\{w_1, \dots, w_n\}$, with $w_j\in\R_{\ge0}$ being the weight of point $p_j$; and $m$ disks given by their radii $\Rr:=\{r_1, \dots, r_m\}$, with $r_j\in\R_{>0}$. 
Additionally, to make the text more clear, we define a set of $m$ disks as $\D = \{D_1, \dots, D_m\}$, with $D_j : \R^2 \mapsto \R^2$ being a function that takes the center where the $j$-th disk is located as input, and returns its coverage region as defined by \autoref{eq:disk}.

@@

@@

In \citeonline{chazelle:1986}, the method for MWC consists on building a planar graph on which the vertices were the $\binom{n}{2}$ pairwise intersection of the circumferences and the edges were the arcs of the circumferences connecting the intersections. With the graph constructed, a traversal is done to obtain the answer, thus the time complexity of $\bigO(n^2)$.

@@

\section{Multiple disks}

In \citeonline{cabello:2006}, a $\bigO(n^{2m-1}\log{n})$ algorithm for $MCD$ is developed as a sub-routine for its $(1-\epsilon)$-approximation algorithm. Firstly, they solve a sub-problem for two disks in $\bigO(n^3\log{n})$. Then, for the rest of the points that are not in that solution, it uses the algorithm developed in \citeonline{chazelle:1986} for the one-disk case, checking every possible solution for every one of the disks left.

\subsection{An algorithm for MCD}

@@

\begin{lema}
	Suppose that an instance of MCD and an index $j\in\{1, \dots, m\}$ are given.
	Then \autoref{algoritmo:mcd_cls}, when given the instance $(\Pp, \Ww, r_j)$ as input, returns a CLS $S_j$ of size $\bigO(n^2)$, such that $q^*_j\in S_j$, with $(q^*_1, \dots, q^*_m)$ being an optimal solution of the given MCD's instance.
\end{lema}

>>>>

An instance of MCD is given by a set of $n$ demand points $\Pp:=\{p_1, \dots, p_n\}$, with $p_j\in\R^2$; a set of weights $\Ww:=\{w_1, \dots, w_n\}$, with $w_j\in\R_{\ge0}$ being the weight of point $p_j$; and $m$ disks given by their radii $\Rr:=\{r_1, \dots, r_m\}$, with $r_j\in\R_{>0}$. 
Additionally, to make the text more clear, we define a set of $m$ disks as $\D:=\{D_1, \dots, D_m\}$, with $D_j : \R^2 \mapsto \R^2$ being a function that takes the center where the $j$-th disk is located as input, and returns its coverage region as defined by \autoref{eq:disk}.

@@

\section{Related Work}
In \citeonline{cabello:2006}, a $\bigO(n^{2m-1}\log{n})$ algorithm for $MCD$ is developed as a sub-routine for its $(1-\epsilon)$-approximation algorithm. Firstly, they solve a sub-problem for two disks in $\bigO(n^3\log{n})$. Then, for the rest of the points that are not in that solution, it uses the algorithm developed in \citeonline{chazelle:1986} for the one-disk case, checking every possible solution for every one of the disks left.

@@

In \citeonline{chazelle:1986}, the method for MWC consists on building a planar graph on which the vertices are the $\binom{n}{2}$ pairwise intersection of the circumferences and the edges are the arcs of the circumferences connecting the intersections. With the graph constructed, a traversal is done to obtain the answer, thus the time complexity of $\bigO(n^2)$.

@@

\section{An algorithm for MCD}

@@

\begin{lema}\label{lema:mcd}
	Suppose that an instance of MCD and an index $j\in\{1, \dots, m\}$ are given.
	Then \autoref{algoritmo:mcd_cls}, when given the instance $(\Pp, \Ww, r_j)$ as input, returns a CLS $S_j$ of size $\bigO(n^2)$, such that $q^*_j\in S_j$, with $(q^*_1, \dots, q^*_m)$ being an optimal solution of the given MCD's instance.
\end{lema}

### 2020-01-23 defesa/tex/chapter/mcer.tex
wip

After that, we define \autoref{algoritmo:mcer} which takes an instance $(\Pp, \Ww, \Rr)$ of MCER, and returns an optimal solution for it.

@@

@@

		\Procedure{$MCER$}{$\Pp, \Ww, \Rr, j=1$}
		\If{$j = m+1$}
		\State \Return $0$
		\EndIf

		\State $ans \gets 0$
		\State Let $(q_{j}^*, \dots, q_m^*); (\theta_{j}^*, \dots, \theta_m^*)$ be the optimal solution, initially set to $0$.

		\State $S_j \gets MCE_1(\Pp, a_j, b_j)$

		\For{$(q_j, \theta_j) \in S_j$}
		\State $Cov \gets \Pp \cap E_j(q_j, \theta_j)$
%		\State $((q_{j+1},\theta_{j+1}); \dots; (q_m, \theta_m)) \gets  MCE(\Pp\setminus Cov, \Ww, \Rr, j+1)\}$

		\State $(q_{j+1}, \dots, q_m); (\theta_{j+1}, \dots, \theta_m) \gets  MCE(\Pp\setminus Cov, \Ww, \Rr, j+1)$

@@

\begin{proof}
	For every $j\in\{1, \dots, m\}$, let $Z \subset \Pp$ be the set of covered points by ellipses $1, \dots, j-1$. 
	Unless $Z=\Pp$, when choosing the center and angle of rotation for the $j$-th ellipse, \autoref{algoritmo:mcer} does not consider $(q_j, \theta_j) \in S_j$, such that $\Pp \cap E_j(q_j, \theta_j) \subset Z$. Apart from those solutions, which are non-optimal, \autoref{algoritmo:mcer} considers every solution in $\Omega(\Pp, \Ww, \Rr)$.
\end{proof}

>>>>

After that, we define \autoref{algoritmo:mcer} which takes an instance $(\Pp, \Ww, \Rr)$ of MCER, and returns an optimal solution for it.
Even though it is based on \autoref{th:mcer}, the set of solutions $\Omega(\Pp, \Ww, \Rr)$ is not explicitly built in \autoref{algoritmo:mcer}. Instead, a complete search is done by backtracking the CLS of every ellipse returned by procedure $MCER_1$.

Two procedures are defined in \autoref{algoritmo:mcer}. The first one, called $MCER$, returns an optimal solution for an instance $(\Pp, \Ww, \Rr)$ using the second procedure $MCER_{bt}$. This second procedure is responsible for the backtracking and takes two additional parameters $j\in\{1, \dots, m\}$, which represents the index of the ellipse that $MCER_{bt}$ is currently processing, and $Z\subset \Pp$, which represents the set of points that have not been covered by the ellipses already processed by $MCER_{bt}$.

@@

		\item[]
		\Procedure{$MCER$}{$\Pp, \Ww, \Rr$}
		\State \Return $MCER_{bt}(\Pp, \Ww, \Rr, 1)$
		\EndProcedure

@@

		\Procedure{$MCER_{bt}$}{$Z, \Ww, \Rr, j$}
		\If{$j = m+1$}
		\State \Return $0$
		\EndIf

		\State $ans \gets 0$
		\State $(q_{j}^*\gets 0, \dots, q_m^*\gets0); (\theta_{j}^*\gets 0, \dots, \theta_m^*\gets 0)$ \Comment{Setting to $0$ as a default value.}

		\State $S_j \gets MCER_1(Z, a_j, b_j)$

		\For{$(q_j, \theta_j) \in S_j$}
		\State $Cov \gets \Pp \cap E_j(q_j, \theta_j)$

		\State $(q_{j+1}, \dots, q_m); (\theta_{j+1}, \dots, \theta_m) \gets  MCER_{bt}(Z\setminus Cov, \Ww, \Rr, j+1)$

@@

\begin{proof}
	For every $j\in\{1, \dots, m\}$, unless $Z=\{\}$, when choosing the center and angle of rotation for the $j$-th ellipse, \autoref{algoritmo:mcer} does not consider any $(q_j, \theta_j) \in \R^2 \times \R$, such that $Z \cap E_j(q_j, \theta_j) = \{\}$. Apart from those solutions, which are non-optimal, \autoref{algoritmo:mcer} considers every solution in $\Omega(\Pp, \Ww, \Rr)$.
\end{proof}

\subsection{Adding facility cost}
